Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-20 main.tex
minor fix

We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
A brufe-force search easily enumerates all the (reptition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.

@@

The computation becomes more demanding in dimension three. 
Enumerating all the shortest-path trees of the triangulations above is feasible but takes considerably longer. 
Brute-force enumeration of all shellings seems infeasible, though, due to the combinatorial explosion of the number of possible shellings. 
Instead, we perform a greedy backtracking search: 
starting with a single simplex, we successively increase the number of shellings until a complete shelling is found. 
Among the possible candidate simplices, we prioritize those that introduce the smallest possible geometric constant. 
We moreover prioritize the completion of face stars, since the induced constants are easier to control via Lemma~\ref{lemma:volumecomparison}. 
It is imperative for the improvement of our upper bounds that we compute the relevant geometric parameters, such as heights, individually for each simplex and use individualized estimates for each of the geometric transformations, thus avoiding overtly pessimistic blanket estimates.

This greedy backtracking algorithm does generally not guarantee that the optimal shelling is found before the last iteration. 
Our implementation starts with a fixed simplex and generates up to $10$ shellings. 
We repeat this for a possible choices of initial simplex, and pick the optimal among those.
The candidate shellings that we obtain in this manner allow for estimates that differ by a factor of about $2$.

>>>>

We compare the reference Neumann eigenvalues with the gradient potential estimate in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.
A brufe-force search easily enumerates all the (repetition-free) face-paths between triangles, which allows us to find the best estimate possible estimate with the aforementioned theorem.

@@

The computation becomes more demanding in dimension three. 
Enumerating all the paths between tetrahedra in our example triangulations is feasible but takes considerably longer. 
Brute-force enumeration of all shellings seems infeasible, though. 
Instead,
